A seamless, client-centric programming model for type safe web applications

### 2014-05-05 paper.tex
Dedicated languages solve another problem.

\paragraph{HOP, Links, Ur/Web and others} In addition to solutions which work
within existing languages, there are several languages specifically created to
target the web domain. These languages tend to target not only the client and
server tiers, but the database tier as well. These languages bring many new,
interesting ideas to the table but suffers from not being compatible with any
more established languages.

@@

@@

@@

>>>>

\paragraph{HOP, Links, Ur/Web and others} In addition to solutions which work
within existing languages, there are several languages specifically crafted
targeting the web domain. These languages target not only the client and server
tiers but the database tier as well, and incorporate several interesting new
ideas such as more expressive type systems and inclusion of typed inline XML
code.\ \cite{hop}\cite{links}\cite{urweb} As our solution aims to bring typed,
seamless communication into the existing Haskell ecosystem without language
modifications, these languages solve a different set of problems.

@@

\bibitem[Chlipala (2010)]{urweb}
A. Chlipala. "Ur: statically-typed metaprogramming with type-level record computation." ACM Sigplan Notices. Vol. 45. No. 6. ACM, 2010.

@@

\bibitem[Cooper et al (1999)]{links}
E. Cooper, S. Lindley, P. Wadler, and J. Yallop. Links: Web programming without tiers. In Formal Methods for Components and Objects (pp. 266-296). Springer Berlin Heidelberg, 2007.

@@

\bibitem[Serrano et al (2006)]{hop}
M. Serrano, E. Gallesio, and F. Loitsch. "Hop: a language for programming the web 2. 0." OOPSLA Companion. 2006.
